---
title: "Lab 1: Introduction to Quarto"
author: "Briana Lonappan"
date: "01/12/2025"
format: html
editor: source
embed-resources: true
execute:
  echo: false
  output: true
  error: true

  
---

# Part Two: Exploring Quarto Documents

## Correlation of Vitamin C and Tooth Growth in Guinea Pigs

```{r}
#| eval: false
#| echo: true
#| label: practicing-running-code
# Load a dataset into the R Environment.
data(ToothGrowth)

# Look at the summary of the variables in the dataset.
summary(ToothGrowth)

```

### Check the Data Documentation

*This dataset investigates the effect of Vitamin C on tooth growth in Guinea Pigs.*

*The two supplement delivery methods include OJ (orange juice) and VC (vitamin c).*

*`ToothGrowth` is a data frame with 60 observations and 3 variables.*


## Creating a Plot


```{r}
#| echo: true
#| label: creating-a-plot
#| layout-ncol: 2
#| fig-align: center
#| fig-cap: "Boxplots comparing tooth length by supplement type and dosage."

library(tidyverse)

ggplot(data = ToothGrowth, 
       mapping = aes(x = supp, y = len)) +
  geom_boxplot() +
  labs(x = "Supplement", y = "Length of Teeth (mm)")

ToothGrowth %>% 
  mutate(dose = as.factor(dose)) %>% 
  ggplot(mapping = aes(x = dose, y = len)) +
  geom_boxplot() +
  labs(x = "Dose of Supplement (mg/day)", y = "Length of Teeth (mm)")
```


```{r}
#| label: t-test-toothgrowth
#| echo: true
#| fig-cap: "Two-sample independent t-test comparing tooth length between supplement methods."
t.test(len ~ supp, 
       data = ToothGrowth, 
       alternative = "two.sided", 
       var.equal = FALSE)
```

## Results of the Effect of Vitamin C on Tooth Growth in Guinea Pigs
1. The p-value (~0.06) is greater than 0.05, so we fail to reject the null hypothesis. There isn’t enough evidence to conclude that mean tooth length differs between the OJ and VC groups.

2. The 95% confidence interval for the difference in mean tooth length is [-0.17 mm, 7.57 mm]. Since it includes zero, this supports the conclusion that there is no statistically significant difference in mean tooth length at the 5% level.





